Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-05-03 PaperVictor.tex
No se estaban respetando unos espacios adecuadamente

Finally, Table \ref{tab:table3} shows data from some porous
silicon based ODM's \hl{and quasi-ODM's designed to operate in the NIR
region and their (quasi-) ODB's are compared with those of
the structures analyzed in the present study. The quasi-ODW}
of the structure $S_1$ results 20 nm wider than that reported by Bruyant,
et al. \cite{Bruyant2003} and it is located closer to the visible range. Furthermore,
\hl{the quasi-ODB of the structure $S_3$} begins at 950 nm like the one
synthesized by Estevez, et al. \cite{Estevez2009}; nevertheless, its width extends to 2750
nm. In other words, $S_3$ has a quasi-ODW 3.55 times larger. Moreover, the
ODW of the structure reported by Xifre-Perez, et al. \cite{Xifre2005} represents only 17.6
\% of the \hl{quasi-ODW's of our $S_2$ and $S_3$ structures}. Aditionally, the table
reveals that the porous silicon based
structures $S_2$ and $S_3$ have the widest gap widths, 1.36 times greater than the
largest reported work until now in the NIR region \cite{Wu2021}.
As compared to the previous studies
\cite{Bruyant2003,Estevez2009,Xifre2005,Wu2021,Fink1998}, this work
opens the possibility of generating dielectric multilayered
\hl{structures with large quasi-omnidirectional bands with pairs of
materials that have a relatively low refractive index contrast. To be
fair, we have to remark that, as shown in Table \ref{tab:table3}, the
(quasi-) omnidirectional band widths of the structures compared above
correspond to different angular ranges,
which are defined by instrumental constrictions.}

@@

This project is supported by Consejo Nacional de Ciencia y
Tecnolog\'{i}a through grant No.A-S1-30393(VA), 256243 (DA), C\'{a}tedras
Conacyt program 1577 (DA), and by DGAPA-PAPIIT UNAM under grant IN111119 (LM).
VA acknowledges PRODEP (Sabbatical grant), and
is grateful to ICF where she spent the sabbatical year.
HPA also expresses his gratitude to the Coordinaci\'{o}n
de la Investigaci\'{o}n Cient\'{i}fica de la Universidad
Michoacana de San Nicol\'{a}s de Hidalgo. VCG is grateful to CIICAp
and ICF where he did this work.

>>>>

Finally, Table \ref{tab:table3} shows data from some porous
silicon based ODM's \hl{and quasi-ODM's designed to operate in the NIR
region and their (quasi-) ODB's are compared with those of
the structures analyzed in the present study. The quasi-ODW}
of the structure $S_1$ results 20 nm wider than that reported by Bruyant,
et al. \cite{Bruyant2003} and it is located closer to the visible range. Furthermore,
\hl{the quasi-ODB of the structure $S_3$} begins at 950 nm like the one
synthesized by Estevez, et al. \cite{Estevez2009}; nevertheless, its width extends to 2750
nm. In other words, $S_3$ has a quasi-ODW 3.55 times larger. Moreover, the
ODW of the structure reported by Xifre-Perez, et al. \cite{Xifre2005} represents only 17.6\% 
of the \hl{quasi-ODW's of our $S_2$ and $S_3$ structures}. Aditionally, the table
reveals that the porous silicon based
structures $S_2$ and $S_3$ have the widest gap widths, 1.36 times greater than the
largest reported work until now in the NIR region \cite{Wu2021}.
As compared to the previous studies
\cite{Bruyant2003,Estevez2009,Xifre2005,Wu2021,Fink1998}, this work
opens the possibility of generating dielectric multilayered
\hl{structures with large quasi-omnidirectional bands with pairs of
materials that have a relatively low refractive index contrast. To be
fair, we have to remark that, as shown in Table \ref{tab:table3}, the
(quasi-) omnidirectional band widths of the structures compared above
correspond to different angular ranges,
which are defined by instrumental constrictions.}

@@

This project is supported by Consejo Nacional de Ciencia y
Tecnolog\'{i}a through grant No. A-S1-30393(VA), 256243 (DA), C\'{a}tedras
Conacyt program 1577 (DA), and by DGAPA-PAPIIT UNAM under grant IN111119 (LM).
VA acknowledges PRODEP (Sabbatical grant), and
is grateful to ICF where she spent the sabbatical year.
HPA also expresses his gratitude to the Coordinaci\'{o}n
de la Investigaci\'{o}n Cient\'{i}fica de la Universidad
Michoacana de San Nicol\'{a}s de Hidalgo. VCG is grateful to CIICAp
and ICF where he did this work.
